---
title: "aRcGeo"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{aRcGeo}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Installing aRcGeo

You can install the development version of `aRcGeo` from GitHub with:

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("HarunCelikOtto/aRcGeo")
```

Once installed, load the library with:

```{r setup}
library(aRcGeo)
```

The first time the library is loaded, you should receive a message asking you to have the package `arcgisbinding` loaded already. This is because the functions verifying ArcGIS licenses in `aRcGeo` use the `arcgisbinding` package.

## Initializing an ArcGIS Connection

The main purpose of the `aRcGeo` package is to provide a streamlined process for initializing a connection to ArcGIS and importing the `arcpy` python module at the same time. This is achieved using the `aRcGeo::init_arcpy()` function.

`init_arcpy()` takes one of two string arguments.

-   `conda_env =  "conda environment name"`

-   `python_env_path = "string path to python.exe"`

Since all installations of `arcpy` in ArcGIS Pro use a conda environment, it is easiest to supply the conda environment name as the `conda_env` argument.

You can check the name of your conda environment using `reticulate::conda_list()`.

```{r}

# List your conda environments with Reticulate

# install.packages("reticulate")
reticulate::conda_list() |> 
  as.list() |> 
  magrittr::extract2(1)
```

## Calling `init_arcpy()`

After confirming the name of the conda environment where `arcpy` exists, we can call `init_arcpy()` to initialize an ArcGIS connection:

```{r}
aRcGeo::init_arcpy(conda_env = "arcgispro-py3-DeepLearning")
```

## Examples of `arcpy` Functionality

If the function call completed without an error, then the user should now see `arcpy` as a module in their R Environment. This means that all of the functionality of `arcpy` can now be used in an R session.

Here is a basic call to the `ListEnvironments()` function in `arcypy`.

```{r}
arcpy$ListEnvironments()
```
