---
title: "aRcGeo"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{aRcGeo}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Installing aRcGeo

You can install the development version of `aRcGeo` from GitHub with:

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("HarunCelikOtto/aRcGeo")
```

Once installed, load the library with:

```{r setup}
library(aRcGeo)
```

The first time the library is loaded, you should receive a message asking you to have the package `arcgisbinding` loaded already. This is because the functions verifying ArcGIS licenses in `aRcGeo` use the `arcgisbinding` package.

## Initializing an ArcGIS Connection

The main purpose of the `aRcGeo` package is to provide a streamlined process for initializing a connection to ArcGIS and importing the `arcpy` python module at the same time. This is achieved using the `aRcGeo::init_arcpy()` function.

`init_arcpy()` takes one of two string arguments.

-   `conda_env =  "conda environment name"`

-   `python_env_path = "string path to python.exe"`

Since all installations of `arcpy` in ArcGIS Pro use a conda environment, it is easiest to supply the conda environment name as the `conda_env` argument.

You can check the name of your conda environment using `reticulate::conda_list()`.

```{r}

# List your conda environments with Reticulate

# install.packages("reticulate")
reticulate::conda_list() |> 
  as.list() |> 
  magrittr::extract2(1)
```

## Calling `init_arcpy()`

After confirming the name of the conda environment where `arcpy` exists, we can call `init_arcpy()` to initialize an ArcGIS connection:

```{r, eval=FALSE}
aRcGeo::init_arcpy(conda_env = "arcgispro-py3-DeepLearning")
```

Output:

``` {r, eval=FALSE}         
-- Initializing Connection ---------------------------------------------------------------------
> Initializing Connection to ArcGIS.

-- Checking Conda Environment ---------------------------------------------------------------------
i All Local Conda Environments:
[1] "base"                       
[2] "Python_Image_Processing"    
[3] "arcgispro-py3-DeepLearning" 
[4] "r-miniconda"               
[5] "r-reticulate"              
v Using conda environment: arcgispro-py3-DeepLearning
v An `arcpy` module successfully imported.                              
i ArcGIS Product Details:   
$license                    
[1] "Advanced"

$version
[1] "13.1.0.41833"

$path
[1] "C:\\Program Files\\ArcGIS\\Pro\\"

$dll
[1] "rarcproxy_pro"

$app
[1] "ArcGIS Pro"

$pkg_ver
[1] "1.0.1.300"
```

## Examples of `arcpy` Functionality

If the function call completed without an error, then the user should now see `arcpy` as a module in their R Environment. This means that all of the functionality of `arcpy` can now be used in an R session.

Here is a basic call to the `ListEnvironments()` function in `arcypy`.

```{r, eval=FALSE}
arcpy$ListEnvironments()
```

Output:

```{r, eval=FALSE}
 [1] "autoCommit"                      "XYResolution"                   
 [3] "processingServerUser"            "gpuId"                          
 [5] "XYDomain"                        "processingServerPassword"       
 [7] "scratchWorkspace"                "recycleProcessingWorkers"       
 [9] "cartographicPartitions"          "terrainMemoryUsage"             
[11] "MTolerance"                      "compression"                    
[13] "coincidentPoints"                "baUseDetailedAggregation"       
[15] "timeZone"                        "randomGenerator"                
[17] "outputCoordinateSystem"          "rasterStatistics"               
[19] "transferGDBAttributeProperties"  "ZDomain"                        
[21] "cellSizeProjectionMethod"        "maintainCurveSegments"          
[23] "transferDomains"                 "S100FeatureCatalogueFile"       
[25] "maintainAttachments"             "resamplingMethod"               
[27] "snapRaster"                      "cartographicCoordinateSystem"   
[29] "baNetworkSource"                 "configKeyword"                  
[31] "matchMultidimensionalVariable"   "outputZFlag"                    
[33] "qualifiedFieldNames"             "tileSize"                       
[35] "annotationTextStringFieldLength" "parallelProcessingFactor"       
[37] "pyramid"                         "referenceScale"                 
[39] "processingServer"                "extent"                         
[41] "unionDimension"                  "XYTolerance"                    
[43] "daylightSaving"                  "tinSaveVersion"                 
[45] "nodata"                          "MDomain"                        
[47] "cellSize"                        "outputZValue"                   
[49] "outputMFlag"                     "cellAlignment"                  
[51] "geographicTransformations"       "ZResolution"                    
[53] "mask"                            "processorType"                  
[55] "maintainSpatialIndex"            "preserveGlobalIds"              
[57] "workspace"                       "retryOnFailures"                
[59] "MResolution"                     "baDataSource"                   
[61] "ZTolerance"                      "scratchGDB"                     
[63] "scratchFolder"                   "packageWorkspace"               
[65] "scriptWorkspace"                 "addOutputsToMap"                
[67] "buildStatsAndRATForTempRaster"   "autoCancelling"                 
[69] "isCancelled"                     "overwriteOutput"  
```

